Studies of quantum dots

### 2016-10-24 Manuscript/paper.tex
Update spEnergiesQD/Manuscript/paper.tex
See also: last pargraph in §4.4 of Heiko's paper
https://arxiv.org/pdf/1512.06956v1.pdf

Compared to Wegner's canonical generator, where the final flow equations involve cubes of the one-body and two-body Hamiltonian matrix elements, these elements contribute only linearly with White's generator, which results in much better numerical properties.  [[It is not explained at all what ``final flow equations'' means]]

>>>>

Compared to Wegner's canonical generator, where the derivative of the final flow equations contain cubes of the Hamiltonian matrix elements (i.e.\ each term contains a product of 3 one-body and/or two-body matrix elements), the elements in White's generator contribute only linearly with White's generator.  This has reduces the stiffness in the differential equation, providing a net increase in computational efficiency since stiff ODE solvers tend to be slower and require more memory.
